Water Quality and Safety at Toronto Beaches

### 2024-09-24 starter_folder-main/paper/paper.qmd
update some changes

There are over 18,000 daily observations of beach conditions in this dataset.

In the following section, I chose six key environmental variables to examine in depth: date, beach name, wind speed, air temperature, water temperature, and bird populations. The analysis is based on observations of over 18,000 daily beach conditions from the Toronto Open Data Portal. By using these variables, we explore how environmental factors affect beach safety and availability. Specifically, we examined the relationship between wind speed and water quality, bird populations and water pollution risk, and how temperature variations affect the overall beach experience. This analysis will help to better plan and communicate the safety and attractiveness of Toronto's beaches.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-his2
#| fig-cap: "Distribution of water temperature"

# 5.Histogram: Distribution of water temperature
water_temp_hist <- ggplot(cleaned_data, aes(x = waterTemp)) +
  geom_histogram(binwidth = 20, fill = "blue", color = "black") +
  labs(x = "Water Temperature (°C)", y = "Count") +
  theme_minimal()

# Print plot and caption
print(water_temp_hist)

>>>>

There are over 18,000 daily observations of beach conditions in this dataset. In the following section, I chose six key environmental variables to examine in depth: date, beach name, wind speed, air temperature, water temperature, and bird populations. By using these variables, we explore how environmental factors affect beach safety and availability. Specifically, we examined the relationship between wind speed and water quality, bird populations and water pollution risk, and how temperature variations affect the overall beach experience. This analysis will help to better plan and communicate the safety and attractiveness of Toronto's beaches. Structure is inspired mainly by @rohan.

@@

# Discussion{#third}
##
